PANCHANGE_analysis

### 2020-08-24 PANCHANGE_analysis.Rmd
phq and ocir stratification

```{r}
dat %>%
  freq(gad.pandemic_felt_feelings_numeric)
```

@@

@@

>>>>

@@

### Split sample in improvement and worsening
```{r phq improvment worsening stratification}
dat <- dat %>%
  mutate(phq.change_binary_numeric =
           case_when(
             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
             phq.pandemic_felt_feelings_numeric == 5 ~ 2
           )
  )

dat <- dat %>%
  mutate(phq.change_binary =
           recode_factor(
             phq.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
  )

dat %>%
  freq(phq.change_binary)
```

@@

### Split sample in improvement and worsening
```{r ocir improvment worsening stratification}
dat <- dat %>%
  mutate(ocir.change_binary_numeric =
           case_when(
             ocir.pandemic_felt_feelings_numeric == 1 ~ 1,
             ocir.pandemic_felt_feelings_numeric == 2 ~ 1,
             ocir.pandemic_felt_feelings_numeric == 3 ~ 0,
             ocir.pandemic_felt_feelings_numeric == 4 ~ 2,
             ocir.pandemic_felt_feelings_numeric == 5 ~ 2
           )
  )

dat <- dat %>%
  mutate(ocir.change_binary =
           recode_factor(
             ocir.change_binary_numeric,
             `1` = "Worsening",
             `2` = "No change",
             `3` = "Improvement"
           )
  )

dat %>%
  freq(ocir.change_binary)
```
